---
title: "Yu_Guo_hw2"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(purrr)
```

#1) Enter and run USArrests. What type of information is shown in the data table USArrests?  (Three or four sentences) The USArrests data set is a data frame which shows the arrest rates based on different states.The length of this data set is 4, The variables in this data set are  "double" "integer".

```{r}
USArrests

typeof(USArrests)
typeof(USArrests$Murder)
typeof(USArrests$Assault)
typeof(USArrests$UrbanPop)
typeof(USArrests$Rape)

length(USArrests)
summary(USArrests)
```



#2) Use and show R coding that features a map function to show maximum values for all variables of the USArerests data frame.  Which State has the largest number of Assaults according to the USAressts data frame?

```{r}
USArrests %>%
  map_dbl(max)


USArrests[which(USArrests$Assault == 337), ]

which(grepl(337, USArrests$Assault))
which(USArrests$Assault == 337, arr.ind = T)
```



#3) Install the nycflights13 package: install.packages("nycflights13") , call the following library:  library(nycflights13), and then enter flights (this will produce the flights data table)

```{r}
library(nycflights13)
flights

```

#4) Use and show R code that will indicate how many rows and how many columns the flights data has.  Review and revisit your notes from STAT 412/612.  Describe a tibble (two or three sentences). Now use and show R code that verifies that flights is a tibble

```{r}

#Tibbles are a modern take on data frames. They keep the features that have stood the test of time, and drop the features that used to be convenient but are now frustrating (i.e. converting character vectors to factors).
?tibble

nrow(flights)
ncol(flights)
class(flights)
```

#5) Now Use and show R code (featuring a map function) that will output the type of each column of the flights tibble.

```{r}

output <- vector("list", ncol(nycflights13::flights))
names(output) <- names(nycflights13::flights)
for (i in names(output)) {
  output[[i]] <- typeof(nycflights13::flights[[i]])
}
output
```

#6)  Use and show R coding that features usage of a map function to find the slope and the intercept of models for the different levels of the Species variable of the iris data frame.  For each model, Sepal.Width predicts Sepal.Length.

```{r}

iris

factor(iris$Species)

models <- iris %>%
  split(.$Species) %>%    #Sepal.Width predicts Sepal.Length.
  map(~lm(Sepal.Length ~ Sepal.Width, data = .))
models

# Now lets get more detailed information for each model.

models %>%
  map(summary) 


```

#7)For the given list above;
#7a) Use and show R code to find the length of the list
#7b) Use and show R code that will extract the missing value
#7c) Use and show R code that will extract the third object
#7d) Use and show R code that will extract the character string and the minimum number.
#7e) Use one line of code to show that the seventh object is a character object.


```{r}
V <- list(12, 22, 27, 31.5, NA, 39, "east")
V
```


```{r}
length(V)
```


```{r}
str(V[is.na(V)])
str(V[[5]])
```


```{r}
str(V[[3]])
```


```{r}

str(V[c(1,7)])
```


```{r}
typeof(V[[7]])
```





